\documentclass[journal]{IEEEtran}
\usepackage{epsf,cite,amsmath,amscd,graphics,graphicx,latexsym,multicol,setspace}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{scalefnt}
\newcounter{MYtempeqncnt}
\begin{document}
\title{Low-Dose CT Image denoising and Restoration using General Adversarial Networks}

\author{Kevin Freire $|$ kfreirea@ryerson.ca\\
Walter Freire $|$ andrei.freire@ryerson.ca \\
Department of Electrical and Computer Engineering\\
Ryerson University, Toronto, Canada.}
\maketitle


% ABSTRACT
\begin{abstract}



\end{abstract}

% KEYWORDS
\begin{IEEEkeywords}
Image restoration, Image Denoising, General Adversarial Networks, GANs, Low-Dose CT, Medical Imagery, Deep Neural Networks.
\end{IEEEkeywords}

% INTRODUCTION
\section{Introduction}
\label{Introduction}
Computerize Tomography (CT) has enabled direct imaging on the 3-dimensional structure of different organs and tissues inside the human body in a non-invasive manner. CT scans are constructed by combining the X-ray scans taken on several angles and orientations.  It has several utilities but very useful in detecting lesions, tensions, tumours, and metastasis.  It can reveal their presence and the spatial location, size and extent of the tumour.  CT imaging has become a frequent tool for cancer diagnosis, angiography, and detecting internal injuries.  However, despite the evidence of its utility for diagnosis and patient management, the potential risk of radiation-induced malignancy exists \cite{brenner2007computed}.  Studies found that CT alone contributes to almost half of the total radiation exposure from medical use alone.  Recent studies reveal that as much as 1.2 - 2\% of cancers may eventually be caused by the radiation dose conceived by the patient while undergoing CT scans \cite{schauer2009national}.  To reduce the risk, the principles of ALARA (As Low As Reasonably Achievable) is now a profound practice predicted in CT imaging \cite{protection2007icrp}.  In regards to this practice, Low Dose CT (LDCT) is a promising solution in reducing radiation exposure \cite{trattner2014standardization}.  In low dose CT, radiation exposure is decreased by lowering the tube current, or voltage.  However, by reducing the tube voltage or current it introduces several artefacts and lowers the diagnostic quality of the LDCT image \cite{boas2012ct}.  In order to boost the quality of an LDCT image, the reconstruction of LDCT has become a primary research.  There are various methods that can be classified under three categories: (a) iterative reconstruction, (b) sinogram filtration based techniques, and (c) image post-processing based technique.  In recent times, researchers were trying to develop new iterative algorithms (IR) for LDCT image reconstruction.  Iterative reconstruction algorithms considerably suppresses the image noise, but still lose some details and suffer from remaining artefacts.  Other disadvantages with IR techniques is the high computational cost, which is a bottle neck in practical utilization.  Sinogram filtration on the other hand, directly works on the projection data before reconstructing the image and is more computationally economical than the IR technique.  However, the data of commercial scanners are not readily available to users, and this method suffers from edge blurring and the resolution loss.  Many efforts were made in the image domain to reduce LDCT noise and suppress artefacts.\\
With the explosive evolution of deep neural networks, the LDCT denoising task is now dominated by deep neural networks.  However, the research on deep learning-based LDCT denoising is confined to designing a network architecture based on the vanilla convolution operation.  There has been a surge in interest in desinging General Adversarial Networks (GAN), mainly for image generation and becoming popular in denoising medical images as shown in \cite{8340157}, \cite{9474492}, \cite{yin2021unpaired}.  In this paper we explore the possibility of applying GAN to the task of LDCT desnoising.\\
	In many image-related reconstruction tasks, it is known that minimizing the per-pixel loss between the output image and the ground truth alone generate either blurring or makes the result visually unappealing \cite{huang2017beyond}.  The same effect was observed in the traditional neural network-based CT denoising works \cite{chen2017low}, \cite{chen2017low2}.  The adversarial loss introduced by GAN can be treated as a driving force to push the generated image to look as close to as the groung truth image or in this case the Normal Dose CT image (NDCT) which also reduces the blurring effect. Further more, an additional perceptual loss was also introduced to measure the feature of the denoised image, with a focus on areas that the human eye cannot see. \\
Generative Adversarial Network was first introduced in 2014 by Goodfellow \emph{et al}. \cite{goodfellow2014generative}.  It is a genrative model trying to generate real world images by employing a min-max optimization framework where two networks (Generator G and Discriminator D) are trained against each other.  G tries to synthesize real appearing images from random noise wheras D is trying to distiguish between the generated and real images.  If the Generator G get sufficiently well trained, the Discriminator D will eventually be unable to tell if the generated image is fake or not.\\
	The original setup of GAN does not contain any constraints to control what modes of data it can generate.  However, the auxiliary information were provided during the generation, GAN can be driven to output images with specific modes.  In this scenario, GAN is usually referred to as conditional GAN (cGAN) since the output is conditioned on additional information.  Bera \emph{et al}. \cite{9474492} proposed a discriminator function for CT denoising task, which leverages self-attention and pixel-wise GANs for restoring the diagnostic quality of LDCT images.  Yi \emph{et al}. \cite{yi2018sharpness}. propsed an adversarial trained network and a sharpness detection network to denoise LDCT images. Both \cite{8340157} and \cite{yin2021unpaired} used Wasserstein GAN with Perceptual Loss and Wasserstein Distance to generate a denoised image of an LDCT image. \\
	In this paper, we make the following contributions:
	
	\begin{enumerate}
		\item We built a GAN architecture similar to Alsaiari \emph{et al}. \cite{alsaiari2019image}. with the exception of trianing it pecifically on LDCT images.
		\item Computed similar loss functions as \cite{alsaiari2019image} with the exception of using the Mean Squared Error Loss function instead of computing L2-norm.
		\item Present the output results of the network after training.
	\end{enumerate}
	
	The remainder of this paper is organized as follows.  The proposed method based on \cite{alsaiari2019image}, with perceptual loss, pixel-pixel loss, smooth loss and adversarial loss are presented in \ref{method}.  Then, experiments and analysis of the results are presented in section \ref{experiment settings} and \ref{results and discussion}.  Lastly, Section \ref{conclusion} gives a summary of this paper and looks forward to some possible future research directions.


\cite{8340157} Yang \emph{et al} - Low-Dose CT Image Denoising Using a Generative Adversarial Network With Wasserstein Distance and Perceptual Loss

\cite{9474492} Bera \emph{et al} - Noise Conscious Training of Non Local Neural Network Powered by Self Attentive Spectral Normalized Markovian Patch GAN for Low Dose CT Denoising

\cite{yin2021unpaired} Yin \emph{et al} - Unpaired Image Denoising via Wasserstein GAN in Low-Dose CT Image with Multi-Perceptual Loss and Fidelity Loss

\cite{radford2015unsupervised} Radford \emph{et al}. - UNSUPERVISED REPRESENTATION LEARNING WITH DEEP CONVOLUTIONAL GENERATIVE ADVERSARIAL NETWORKS

\cite{chen2017low} Chen \emph{et al}. - Low-dose ct via deep neural network

\cite{chen2017low2} Chen \emph{et al} - Low-dose CT with a residual encoder-decoder convolutional neural network

\cite{huang2017beyond} Huang \emph{et al}. - Beyond face rotation: Global and local perception gan for photorealistic and identity preserving frontal view synthesis

\cite{goodfellow2014generative} Goodfellow \emph{et al}. - Generative adversarial nets

\cite{yi2018sharpness} Yi \emph{et al}. - Sharpness-aware low-dose CT denoising using conditional generative adversarial network

% METHOD
\section{Method}
\label{method}
	We built a GAN network structure for image denoising, which like, \cite{alsaiari2019image}, is based on ResNet \cite{he2016deep}.  A generator network is trained to generate noise fre images through comptition with the discriminator network, using ground truth NDCT images to imporve the quality of the generated images.  Our network makes use of residual blocks, skip connections, and batch normalization.  Due to training limitations, we used three residual blocks.  However, having a larger number of residual blocks would increase the training accuracy significantly, but with a higher computational complexity and longer training times.\\
	Suppose that $z \in \{z_k\}_1^N$ denotes the LDCT image, $x \in \{x_k\}_1^N$ denotes the NDCT image, and $p_l$ and $p_r$ represent the distribution of LDCT and NDCT images, respectively.  The generator G learns a mapping $G: z \rightarrow \hat{x}$, where \emph{z} is the LDCT the generator is conditioned upon.  $\hat{x}$ is the denoised CT that is expected to be as close to as the NDCT image \emph{x}.  The discriminator D, is to differentiate the generated image \emph{z} from the real \emph{x}.  
	
% LOSS FUNCTION
\subsection{Refined Loss Function}
\label{loss function}
In the original GAN \cite{goodfellow2014generative}, D and G are trained by solving the following minmax problem\\

\begin{equation}
	\mathop{min}_{G}\mathop{max}_{D} L_{GAN}(D,G) = -E_{x \tilde p_r}[D(x)] + E_{z \tilde p_l}[1-D(G(z))]
\end{equation}

where $E(\cdot)$ denotes the expectation operator.  The generator G transforms a noisy sample to mimic a real sample, which defines a data distribution, denoted by $p_g$.  Then D is trained to become an optimal discriminator for a fixed G, the minimization search for G is equivalent to minimizing the Jensen-Shannon (JS) divergence of $p_r$ and $p_g$, which will lead to a vanished gradient on the Generator G  \cite{8340157} and G will stop updating as the training continues.

% GENERATOR NETWORK
\subsection{Generator Network}
\label{generator}
The goal of a single image denoising is to generate a realistic image with high quaility.  The 

% DISCRIMINATOR NETWORK
\subsection{Discriminator Network}
\label{discriminator}


% EXPERIMENT SETTINGS
% this section includes dataset and training details
\section{Experiment Settings}
\label{experiment settings}

% RESULTS AND DISCUSSIONS
\section{Results and Discussion}
\label{results and discussion}

% COMPUTATIONAL COMPLEXITY
\section{Computational Complexity}
\label{complexity}

% CONCLUSION
\section{Conclusion}
\label{conclusion}

% REFERENCES
\bibliography{project_reference}
\bibliographystyle{ieeetr}
\end{document}